---
title: "Reproducible documents"
author: "MP"
format: html
editor: visual
---

```{r first-code}
2+2
```

```{r variable}
weight_kilos<-100
weight_kilos
```

```{r test}
# Character vector
c("a", "b", "c")
# Logic vector
c(TRUE, FALSE, FALSE)
# Numeric vector
c(1, 5, 6)
# Factor vector (special types of character vectors)
factor(c("low", "high", "medium", "high"))
```

```{r setup}
#| message: false
#| warning: false
library(tidyverse)
post_meal_data <- read_csv2(here::here("data/post-meal-insulin.csv"))

```

```{r markdown}
# 
```

# Header 1

Paragraph.

## Header 2

Paragraph.

### Header 3

Paragraph.

*hello* **hello** he^ll^o he~ll~o

-   hi
-   hello
-   hej

## About me

-   Mathilde Palmier
-   Postdoctoral researcher
-   Southern Denmark University

I am a *scientist* and a **dancer**

## Simple code

```{r}
3*3

```

## Testing for Git

Hello I am learning how to use R

## showing the data meal-insulin

```{r}
post_meal_data
glimpse(post_meal_data)
```

## Plot one continuous data

```{r}
#|fig-cap: "Distribution of BMI."
#| label: fig-bmi-histo
ggplot(post_meal_data, aes(x = BMI)) +
   geom_histogram()

```

##Exercise: Plot discrete variable

```{r}
#| fig-cap: "glykemi"
#| label: fig-group-histo
ggplot(post_meal_data, aes(x =glykemi))+
geom_bar()

```

See @fig-group-histo above for a cool plot!

## Plorting two discrete variables

```{r}
ggplot(post_meal_data, aes(x = Group, fill = glykemi)) +
  geom_bar()
```

```{r}

ggplot(post_meal_data, aes(x = Group, fill = as.character(glykemi))) +
  geom_bar()+
  labs(title ="Graph", y="number of participants", fill="glykemi")
  
  
```

```{r}

ggplot(post_meal_data, aes(x = Group, fill = as.character(glykemi))) +
  geom_bar(position = position_dodge())+
  labs(fill="glykemi", y="number of participants")
```

```{r side by side figs}

#| label: fig-bmi-glycemia
#| fig-cap: "BMI and glycemia, side by side."
#| fig-subcap:
#|   - "Distribution of BMI."
#|   - "Number of those with glycemia."
#| layout-ncol: 2
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()

ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()

```
```{r}
#| label: fig-bmi-glycemia
#| fig-cap: "BMI and glycemia, side by side."
#| fig-subcap:
#|   - "Distribution of BMI."
#|   - "Number of those with glycemia."
#| layout-ncol: 2
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()

ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

